Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2023-12-15 introduction.tex
Intro structure

@@

\section{Durations} \label{inc-prev:sec:duration}

@@

>>>>

\documentclass[thesis.tex]{subfiles}

\begin{document}

\chapter{Introduction} \label{intro}

\section{The COVID-19 pandemic and ongoing burden}

\section{SARS-CoV-2 and COVID-19}

Viral loads are infrequently measured exactly.
The most common form of data obtained is cycle threshold (Ct) values from real-time quantitative  reverse-transcriptase polymerase chain reaction (PCR) tests.
The Ct value is proportional to the negative log of the viral load which is convenient when modelling log viral load as a piecewise linear function, since Ct values themselves are piecewise linear under this assumption.
When a host's viral load is too low (below the limit of detection of the PCR test), no Ct value is available and hence viral load can be considered censored at the limit of detection.
The relationship between Ct and viral load is noisy and can vary based on many factors including quality of swab obtained, primers used (even between batches), and the PCR system set-up~\autocites{dahdouhCt,hanRTPCR}.

@@

\section{Duration} \label{inc-prev:sec:duration}

@@

\section{Thesis outline}

\end{document}

### 2023-12-15 thesis.tex
Most simulation results for imperfect testing
First version of full text on imperfect testing
Full first draft of imperfect chapter
Good looking bibliography
Add backcalc chapter
Fix todo location
deal with comments
Intro structure

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{floatpag}
\usepackage{bm}
\usepackage{algorithm2e}
\usepackage[nameinlink]{cleveref}
\usepackage[style=british]{csquotes}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{textcomp} % provide symbols
\usepackage{todonotes}
\usepackage{xr}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{caption}
% \usepackage{microtype}
\usepackage[UKenglish]{babel}

@@

% Only number labelled equations
% \forlistloop workaround due to incompatability with biblatex
% See: https://tex.stackexchange.com/questions/220268/biblatex-and-autonum-dont-work-together
\usepackage{etoolbox} % get the good meaning of \forlistloop
\let\etoolboxforlistloop\forlistloop % save the good meaning of \forlistloop
\usepackage{autonum}
\let\forlistloop\etoolboxforlistloop % restore the good meaning of \forlistloop
\makeatletter
\let\blx@noerroretextools\empty
\makeatother
\usepackage[backend=biber,style=authoryear,uniquename=false,sortcites=true,maxcitenames=2,sorting=ynt,style=apa]{biblatex}
\addbibresource{references.bib}
% Display a linked DOI
\DeclareFieldFormat{doi}{%
  \mkbibacro{DOI}\addcolon\space
  \ifhyperref
    {\href{https://doi.org/#1}{\nolinkurl{#1}}}
    {\nolinkurl{#1}}%
}

\usepackage{subfiles} % Best loaded last in the preamble
\addbibresource{references.bib}
\externaldocument[E-]{\subfix{thesis}}

@@

\usepackage{geometry}
\setlength{\marginparwidth}{3cm}
\geometry{margin=3.8cm}

@@

\chapter{Introduction} \label{intro}

\section{The COVID-19 pandemic and ongoing burden}

\section{SARS-CoV-2 and COVID-19}

Viral loads are infrequently measured exactly.
The most common form of data obtained is cycle threshold (Ct) values from real-time quantitative  reverse-transcriptase polymerase chain reaction (PCR) tests.
The Ct value is proportional to the negative log of the viral load which is convenient when modelling log viral load as a piecewise linear function, since Ct values themselves are piecewise linear under this assumption.
When a host's viral load is too low (below the limit of detection of the PCR test), no Ct value is available and hence viral load can be considered censored at the limit of detection.
The relationship between Ct and viral load is noisy and can vary based on many factors including quality of swab obtained, primers used (even between batches), and the PCR system set-up~\autocites{dahdouhCt,hanRTPCR}.

\section{Thesis outline}

@@

\chapter{Estimating transmission using backcalculation} \label{backcalc}

@@

@@

\chapter{CIS episode definitions} \label{episode-def}

\todo[inline]{Get this from SARAH}

\end{document}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{floatpag}
\usepackage{bm}
\usepackage{algorithm2e}
\usepackage[nameinlink]{cleveref}
\usepackage[style=british]{csquotes}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{textcomp} % provide symbols
\usepackage{todonotes}
\usepackage{xr}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{caption}
\usepackage{numprint}
% \usepackage{microtype}
\usepackage[UKenglish]{babel}

@@

% Only number labelled equations
% \forlistloop workaround due to incompatability with biblatex
% See: https://tex.stackexchange.com/questions/220268/biblatex-and-autonum-dont-work-together
\usepackage{etoolbox} % get the good meaning of \forlistloop
\let\etoolboxforlistloop\forlistloop % save the good meaning of \forlistloop
\usepackage{autonum}
\let\forlistloop\etoolboxforlistloop % restore the good meaning of \forlistloop
\makeatletter
\let\blx@noerroretextools\empty
\makeatother
\usepackage[backend=biber,uniquename=false,sortcites=true,maxcitenames=2,style=apa]{biblatex}
\addbibresource{references.bib}
% Display a linked DOI
\DeclareFieldFormat{doi}{%
  \mkbibacro{DOI}\addcolon\space
  \ifhyperref
    {\href{https://doi.org/#1}{\nolinkurl{#1}}}
    {\nolinkurl{#1}}%
}

\usepackage{subfiles} % Best loaded last in the preamble
\addbibresource{references.bib}
\addbibresource{refs-custom.bib}
\externaldocument[E-]{\subfix{thesis}}
\externaldocument[E-]{\subfix{output}}

@@

%% REMOVE THESE FOR FINAL VERSION WITHOUT TODOS
\usepackage{geometry}
\setlength{\marginparwidth}{3cm}
\geometry{margin=3.8cm}

@@

\subfile{introduction}

@@

\subfile{backcalc}

@@

\chapter{CIS episode definitions} \label{episode-def}
\todo[inline]{Get this from SARAH}

@@

\cref{perf-test:eq:piu}
\end{document}
